### 2014-12-16 reachability.tex
CLNS format

At the next step $T+1$ we find the new active process resulted from the predicate $activeFromTo$ (line \ref{e4}) as well as all the unchanged processes that correspond to the other sorts (line \ref{e5}).\\
As a result it will be displayed all possible evolutions of the netwoks.
\subsection{Reachability verification}
\begin{itemize}

\item \textbf{known steps number } 
Parler de la méthode qui vérifie l'atteignabilité après un nombre fini de changements
\item \textbf{unknown steps number: incremental approch (iclingo)}
Parler de la méthode qui vérifie l'atteignabilité après un nombre indéfini de changements et qui retourne le chemin le plus court s'il existe pour atteindre ces objectifs
\end{itemize}

>>>>

At the next step $T+1$ we find the new active process resulted from the predicate $activeFromTo$ (line \ref{e4}) as well as all the unchanged processes that correspond to the other sorts (line \ref{e5}).\\
As a result it will be displayed all possible evolutions of the netwoks.
\subsection{Reachability verification}
In this section, we focus on the reachability of a process which corresponds to the question \cite{def:reachability} :\\
“Is it possible, starting from a given initial state, to play a number of actions so that a given processes are active in the resulting state?”

\noindent Now we try to adapt the code of network evolution to resolve the reachability problem. First we define a predicate for the objective processes we call it $"goal"$, we add a rule with this predicate to the script defining the PH :
\begin{lstlisting}
goal(activeProcess("a",1)). %\label{c1}
\end{lstlisting}
The rule line \ref{c1} verifies if after the network evolution, its state satisfies the goals at step $T$. Else the answer will be eliminated.
\begin{lstlisting}
satisfiable(F,T) :-  goal(F), instate(F,T). %\label{c2}
\end{lstlisting}
The limitation of this method is that the user has to choose the number of steps of the evolution. It is an disadvantage because a search in N steps will find no solution if the shortest path to solve the rechability requires N+1 steps. The solution is to use the incremental computation mode ( \textsc{iclingo} \cite{gebser2008user}).
So we have almost the same program expect for incremental step numbers. In each step t, the program computes the playable actions $playableAction(A,I,B,J,K,t)$,the possible change $activeFromTo(B,J,K,t-1)$ and the new active processes for the next step $instate(activeProcess(A,I),t+1)$. Regarding the part of local steps we use a special constraint (rule \textbf{c4}) that means that the program should continue to the next step if it's not satisfiable so that we eliminate responses that do not meet the goals.
\begin{lstlisting}
notSatisfiable(t) :-  goal(F), not instate(F,t). %\label{c3}
:- notSatisfiable(t). %\label{c4}
\end{lstlisting}
